---
title: "ED_5_LAD1_isolation"
date: "2023-11-28"
output: 
  html_document:
    theme: journal #cerulean
    highlight: monochrome
    toc: true
    toc_float: true
    code_folding: show
  editor_options:
    chunk_output_type: console
---

Scripts for all figures in the paper.
This is Extended Data 5

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load libraries
```{r}
suppressWarnings(library(GenomicRanges))
suppressWarnings(library(dplyr))
suppressWarnings(library(stringr))
suppressWarnings(library(readr))
suppressWarnings(library(tidyr))
suppressWarnings(library(ggplot2))
suppressWarnings(library(ggplotify))
library(rtracklayer)
library(IRanges)
library(GenomeInfoDb)
library(tidyverse)
library(ggrastr)
library(gridExtra)
library(colorspace)
library(caTools)
library(RColorBrewer)
library(ggbeeswarm)
library(ggsignif)
library(ggbreak)
library(plyranges)

```


# Load data
```{r}
# Load data
LoadData <- function(samples, directory = "counts", column = "sample", bin_size = "25kb", 
                     results_dir = "/DATA/usr/l.dauban/projects/pA-DamID/E2316_LAD_isolation_reseq") {
  # Simply load the normalized values and return one GRanges object with all
  # the data
  #
  # Input:
  # * samples: samples vector
  # * directory: directory containing the data
  # * column: column name with the sample names
  #
  # Output:
  # * GRanges with data
 
  df.norm <- NULL
 
  for (s in samples) {
   
    # Create the file path of the sample
    df.name <- file.path(results_dir,
                         "results_mm10_nextseq_strainspecific", directory,
                         paste0("bin-", bin_size),
                         paste0(s,
                                ifelse(directory == "normalized",
                                       ".norm.txt.gz",
                                       ".counts.txt.gz")))
   
    # Read the data
    print(df.name)
    df <- read.table(df.name,
                     sep = "\t", stringsAsFactors = FALSE,
                     col.names = c("seqnames", "start", "end", s))
   
    # Add this to one data frame
    if (is.null(df.norm)) {
      df.norm <- df
    } else {
      df.norm <- cbind(df.norm, df[, 4], stringsAsFactors = F)
    }
  }
  
 
  # Add +1 to the start, as this was bed-based
  df.norm[, 2] <- df.norm[, 2] + 1
  
  # Change names
  names(df.norm)[4:ncol(df.norm)] <- samples
 
  # And convert to GRanges
  df.norm <- as(df.norm, "GRanges")
  df.norm
 
}


###################################### Pool 7

samples <- c("Pool3_cl70_1_Dam_CAS-25kb",
             "Pool3_cl70_1_Dam_129S1-25kb",
             "Pool3_cl70_2_Dam_CAS-25kb",
             "Pool3_cl70_2_Dam_129S1-25kb",
             "Pool3_cl83_1_Dam_CAS-25kb",
             "Pool3_cl83_1_Dam_129S1-25kb",
             "Pool3_cl83_2_Dam_CAS-25kb",
             "Pool3_cl83_2_Dam_129S1-25kb",
             "Pool3_cl70_deep_1_Dam_CAS-25kb",
             "Pool3_cl70_deep_1_Dam_129S1-25kb",
             "Pool3_cl70_deep_2_Dam_CAS-25kb",
             "Pool3_cl70_deep_2_Dam_129S1-25kb",
             "Pool3_cl83_deep_1_Dam_CAS-25kb",
             "Pool3_cl83_deep_1_Dam_129S1-25kb",
             "Pool3_cl83_deep_2_Dam_CAS-25kb",
             "Pool3_cl83_deep_2_Dam_129S1-25kb",
             "Pool3_cl70_1_LB1_CAS-25kb",
             "Pool3_cl70_1_LB1_129S1-25kb",
             "Pool3_cl70_2_LB1_CAS-25kb",
             "Pool3_cl70_2_LB1_129S1-25kb",
             "Pool3_cl83_1_LB1_CAS-25kb",
             "Pool3_cl83_1_LB1_129S1-25kb",
             "Pool3_cl83_2_LB1_CAS-25kb",
             "Pool3_cl83_2_LB1_129S1-25kb",
             "Pool3_cl70_deep_1_LB1_CAS-25kb",
             "Pool3_cl70_deep_1_LB1_129S1-25kb",
             "Pool3_cl70_deep_2_LB1_CAS-25kb",
             "Pool3_cl70_deep_2_LB1_129S1-25kb",
             "Pool3_cl83_deep_1_LB1_CAS-25kb",
             "Pool3_cl83_deep_1_LB1_129S1-25kb",
             "Pool3_cl83_deep_2_LB1_CAS-25kb",
             "Pool3_cl83_deep_2_LB1_129S1-25kb",
             "Pool4_cl81_1_Dam_CAS-25kb",
             "Pool4_cl81_1_Dam_129S1-25kb",
             "Pool4_cl81_2_Dam_CAS-25kb",
             "Pool4_cl81_2_Dam_129S1-25kb",
             "Pool4_cl81_deep_1_Dam_CAS-25kb",
             "Pool4_cl81_deep_1_Dam_129S1-25kb",
             "Pool4_cl81_deep_2_Dam_CAS-25kb",
             "Pool4_cl81_deep_2_Dam_129S1-25kb",
             "Pool4_cl81_1_LB1_CAS-25kb",
             "Pool4_cl81_1_LB1_129S1-25kb",
             "Pool4_cl81_2_LB1_CAS-25kb",
             "Pool4_cl81_2_LB1_129S1-25kb",
             "Pool4_cl81_deep_1_LB1_CAS-25kb",
             "Pool4_cl81_deep_1_LB1_129S1-25kb",
             "Pool4_cl81_deep_2_LB1_CAS-25kb",
             "Pool4_cl81_deep_2_LB1_129S1-25kb",
             "Pool7_cl84_1_LB1_CAS-25kb",
             "Pool7_cl127_1_LB1_CAS-25kb",
             "Pool7_cl84_1_LB1_129S1-25kb",
             "Pool7_cl127_1_LB1_129S1-25kb",
             "Pool7_cl84_2_LB1_CAS-25kb",
             "Pool7_cl127_2_LB1_CAS-25kb",
             "Pool7_cl84_2_LB1_129S1-25kb",
             "Pool7_cl127_2_LB1_129S1-25kb",
             "Pool7_cl84_1_Dam_CAS-25kb",
             "Pool7_cl127_1_Dam_CAS-25kb",
             "Pool7_cl84_1_Dam_129S1-25kb",
             "Pool7_cl127_1_Dam_129S1-25kb",
             "Pool7_cl84_2_Dam_CAS-25kb",
             "Pool7_cl127_2_Dam_CAS-25kb",
             "Pool7_cl84_2_Dam_129S1-25kb",
             "Pool7_cl127_2_Dam_129S1-25kb",
             "Pool7_cl84_deep_1_LB1_CAS-25kb",
             "Pool7_cl127_deep_1_LB1_CAS-25kb",
             "Pool7_cl84_deep_1_LB1_129S1-25kb",
             "Pool7_cl127_deep_1_LB1_129S1-25kb",
             "Pool7_cl84_deep_2_LB1_CAS-25kb",
             "Pool7_cl127_deep_2_LB1_CAS-25kb",
             "Pool7_cl84_deep_2_LB1_129S1-25kb",
             "Pool7_cl127_deep_2_LB1_129S1-25kb",
             "Pool7_cl84_deep_1_Dam_CAS-25kb",
             "Pool7_cl127_deep_1_Dam_CAS-25kb",
             "Pool7_cl84_deep_1_Dam_129S1-25kb",
             "Pool7_cl127_deep_1_Dam_129S1-25kb",
             "Pool7_cl84_deep_2_Dam_CAS-25kb",
             "Pool7_cl127_deep_2_Dam_CAS-25kb",
             "Pool7_cl84_deep_2_Dam_129S1-25kb",
             "Pool7_cl127_deep_2_Dam_129S1-25kb",
             "Pool8_cl58_1_LB1_CAS-25kb",
             "Pool8_cl58_1_LB1_129S1-25kb",
             "Pool8_cl58_2_LB1_CAS-25kb",
             "Pool8_cl58_2_LB1_129S1-25kb",
             "Pool8_cl58_1_Dam_CAS-25kb",
             "Pool8_cl58_1_Dam_129S1-25kb",
             "Pool8_cl58_2_Dam_CAS-25kb",
             "Pool8_cl58_2_Dam_129S1-25kb",
             "Pool8_cl58_deep_1_LB1_CAS-25kb",
             "Pool8_cl58_deep_1_LB1_129S1-25kb",
             "Pool8_cl58_deep_2_LB1_CAS-25kb",
             "Pool8_cl58_deep_2_LB1_129S1-25kb",
             "Pool8_cl58_deep_1_Dam_CAS-25kb",
             "Pool8_cl58_deep_1_Dam_129S1-25kb",
             "Pool8_cl58_deep_2_Dam_CAS-25kb",
             "Pool8_cl58_deep_2_Dam_129S1-25kb"
             )


samples <- LoadData(samples)
samples <- samples %>% as_tibble() %>% rowwise() %>% mutate(Pool3_cl70_CAST = sum(Pool3_cl70_1_LB1_CAS.25kb, Pool3_cl70_2_LB1_CAS.25kb, Pool3_cl70_1_Dam_CAS.25kb, Pool3_cl70_2_Dam_CAS.25kb, 
                                                                                  Pool3_cl70_deep_1_LB1_CAS.25kb, Pool3_cl70_deep_2_LB1_CAS.25kb, Pool3_cl70_deep_1_Dam_CAS.25kb, Pool3_cl70_deep_2_Dam_CAS.25kb),
                                                            Pool3_cl70_129S1 = sum(Pool3_cl70_1_LB1_129S1.25kb, Pool3_cl70_2_LB1_129S1.25kb, Pool3_cl70_1_Dam_129S1.25kb, Pool3_cl70_2_Dam_129S1.25kb, 
                                                                                  Pool3_cl70_deep_1_LB1_129S1.25kb, Pool3_cl70_deep_2_LB1_129S1.25kb, Pool3_cl70_deep_1_Dam_129S1.25kb, Pool3_cl70_deep_2_Dam_129S1.25kb),
                                                            Pool3_cl83_CAST = sum(Pool3_cl83_1_LB1_CAS.25kb, Pool3_cl83_2_LB1_CAS.25kb, Pool3_cl83_1_Dam_CAS.25kb, Pool3_cl83_2_Dam_CAS.25kb, 
                                                                                  Pool3_cl83_deep_1_LB1_CAS.25kb, Pool3_cl83_deep_2_LB1_CAS.25kb, Pool3_cl83_deep_1_Dam_CAS.25kb, Pool3_cl83_deep_2_Dam_CAS.25kb),
                                                            Pool3_cl83_129S1 = sum(Pool3_cl83_1_LB1_129S1.25kb, Pool3_cl83_2_LB1_129S1.25kb, Pool3_cl83_1_Dam_129S1.25kb, Pool3_cl83_2_Dam_129S1.25kb, 
                                                                                  Pool3_cl83_deep_1_LB1_129S1.25kb, Pool3_cl83_deep_2_LB1_129S1.25kb, Pool3_cl83_deep_1_Dam_129S1.25kb, Pool3_cl83_deep_2_Dam_129S1.25kb),
                                                            Pool4_cl81_CAST = sum(Pool4_cl81_1_LB1_CAS.25kb, Pool4_cl81_2_LB1_CAS.25kb, Pool4_cl81_1_Dam_CAS.25kb, Pool4_cl81_2_Dam_CAS.25kb, 
                                                                                  Pool4_cl81_deep_1_LB1_CAS.25kb, Pool4_cl81_deep_2_LB1_CAS.25kb, Pool4_cl81_deep_1_Dam_CAS.25kb, Pool4_cl81_deep_2_Dam_CAS.25kb),
                                                            Pool4_cl81_129S1 = sum(Pool4_cl81_1_LB1_129S1.25kb, Pool4_cl81_2_LB1_129S1.25kb, Pool4_cl81_1_Dam_129S1.25kb, Pool4_cl81_2_Dam_129S1.25kb, 
                                                                                  Pool4_cl81_deep_1_LB1_129S1.25kb, Pool4_cl81_deep_2_LB1_129S1.25kb, Pool4_cl81_deep_1_Dam_129S1.25kb, Pool4_cl81_deep_2_Dam_129S1.25kb),
                                                            Pool7_cl84_CAST = sum(Pool7_cl84_1_LB1_CAS.25kb, Pool7_cl84_2_LB1_CAS.25kb, Pool7_cl84_1_Dam_CAS.25kb, Pool7_cl84_2_Dam_CAS.25kb,
                                                                                  Pool7_cl84_deep_1_LB1_CAS.25kb, Pool7_cl84_deep_2_LB1_CAS.25kb, Pool7_cl84_deep_1_Dam_CAS.25kb, Pool7_cl84_deep_2_Dam_CAS.25kb),
                                                            Pool7_cl127_CAST = sum(Pool7_cl127_1_LB1_CAS.25kb, Pool7_cl127_2_LB1_CAS.25kb, Pool7_cl127_1_Dam_CAS.25kb, Pool7_cl127_2_Dam_CAS.25kb,
                                                                                   Pool7_cl127_deep_1_LB1_CAS.25kb, Pool7_cl127_deep_2_LB1_CAS.25kb, Pool7_cl127_deep_1_Dam_CAS.25kb, Pool7_cl127_deep_2_Dam_CAS.25kb),
                                                            Pool7_cl84_129 = sum(Pool7_cl84_deep_1_LB1_129S1.25kb, Pool7_cl84_deep_2_LB1_129S1.25kb, Pool7_cl84_deep_1_Dam_129S1.25kb, Pool7_cl84_deep_2_Dam_129S1.25kb,
                                                                                 Pool7_cl84_deep_1_LB1_129S1.25kb, Pool7_cl84_deep_2_LB1_129S1.25kb, Pool7_cl84_deep_1_Dam_129S1.25kb, Pool7_cl84_deep_2_Dam_129S1.25kb),
                                                            Pool7_cl127_129 = sum(Pool7_cl127_deep_1_LB1_129S1.25kb, Pool7_cl127_deep_2_LB1_129S1.25kb, Pool7_cl127_deep_1_Dam_129S1.25kb, Pool7_cl127_deep_2_Dam_129S1.25kb,
                                                                                  Pool7_cl127_deep_1_LB1_129S1.25kb, Pool7_cl127_deep_2_LB1_129S1.25kb, Pool7_cl127_deep_1_Dam_129S1.25kb, Pool7_cl127_deep_2_Dam_129S1.25kb),
                                                            Pool8_cl58_CAST = sum(Pool8_cl58_deep_1_LB1_CAS.25kb, Pool8_cl58_deep_2_LB1_CAS.25kb, Pool8_cl58_deep_1_Dam_CAS.25kb, Pool8_cl58_deep_2_Dam_CAS.25kb,
                                                                                  Pool8_cl58_deep_1_LB1_CAS.25kb, Pool8_cl58_deep_2_LB1_CAS.25kb, Pool8_cl58_deep_1_Dam_CAS.25kb, Pool8_cl58_deep_2_Dam_CAS.25kb),
                                                            Pool8_cl58_129 = sum(Pool8_cl58_deep_1_LB1_129S1.25kb, Pool8_cl58_deep_2_LB1_129S1.25kb, Pool8_cl58_deep_1_Dam_129S1.25kb, Pool8_cl58_deep_2_Dam_129S1.25kb,
                                                                                 Pool8_cl58_deep_1_LB1_129S1.25kb, Pool8_cl58_deep_2_LB1_129S1.25kb, Pool8_cl58_deep_1_Dam_129S1.25kb, Pool8_cl58_deep_2_Dam_129S1.25kb))

```


# Extended Data 5D - Deletion in the strong iLAD - Pool3
```{r}

## deletion coordinate

del_loc_pool3 = data.frame(sample = c('1', '2'),
           x = c(110927601, 112439588),
           y = rep(1.4, 2),
           xend = c(112653616, 114785359),
           yend = rep(1.4, 2))


# Function
PlotDataTracksLight <- function(input_tib, exp_names, color_groups, 
                                centromeres = NULL, plot_chr = "chr1", 
                                plot_start = 1, plot_end = 500e6,
                                smooth = 1, color_list = NULL,
                                fix_yaxis = F, aspect_ratio = NULL,
                                lighten_negative = F, raster = F) {
  
  # Get the scores for the samples
  tib_plot <- input_tib %>%
    dplyr::select(seqnames, start, end, 
                  all_of(exp_names))
  
  if (smooth > 1) {
    tib_plot <- tib_plot %>%
      mutate_at(vars(contains("_")), 
                runmean, k = smooth)
  }
  
  # Filter for plotting window
  tib_plot <- tib_plot %>%
    filter(seqnames == plot_chr,
           start >= plot_start,
           end <= plot_end)
  
  # Gather
  tib_gather <- tib_plot %>%
    gather(key, value, -seqnames, -start, -end) %>%
    mutate(key = factor(key, levels = exp_names),
           fill_column = color_groups[match(key, names(color_groups))],
           fill_column = factor(fill_column, levels = unique(color_groups)))
  
  # If desired, make negative values a lighter shade to improve visualization
  if (lighten_negative) {
    tib_gather <- tib_gather %>%
      mutate(fill_column = interaction(fill_column,
                                       value < 0))
  }
  
  
  
  # Plot
  ylimits <- quantile(tib_gather$value, c(0.001, 0.999), na.rm = T)
  fill_column <- NULL
  
  plt <- tib_gather %>% 
    ggplot(aes(fill = fill_column))
  
  
  # Set all counts tracks to the same limits
  if (raster) {
    plt <- plt + 
      rasterize(geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                              ymin = 0, ymax = value)),
                dpi = 300)
  } else {
    plt <- plt + 
      geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                    ymin = 0, ymax = value))
  }
  
  plt <- plt + 
    geom_hline(yintercept = 0, size = 0.5) +
    #geom_segment(data=del_loc[1,], mapping=aes(x=x/1e6, xend=xend/1e6, y=y, yend=yend), linewidth = 1, color = "#6BAED6")+
    geom_vline(xintercept = del_loc_pool3[1,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool3[1,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool3[2,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool3[2,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    facet_grid(key ~ ., scales = "free_y") +
    xlab(paste0(plot_chr, " (Mb)")) +
    ylab("counts (Dam + LB1)") +
    #scale_x_continuous(expand = c(0, 0)) + 
    #scale_y_continuous(expand = c(0.025, 0.025), limits = c(-1.5, 1.5)) +
    theme_bw() +
    theme(text = element_text(size = 50))
  
  # Centromeres
  if (! is.null(centromeres)) {
    centromeres.plt <- as_tibble(centromeres) %>%
      filter(seqnames == plot_chr) %>%
      gather(key_centromeres, value, start, end)
    
    plt <- plt +
      geom_line(data = centromeres.plt, 
                aes(x = value / 1e6, y = 0),
                color = "black", size = 2)
  }
  
  if (! is.null(color_list)) {
    
    if (lighten_negative) {
      color_list <- c(color_list,
                      lighten(color_list, amount = 0.5))
    }
    
    colors <- levels(tib_gather$fill_column)
    
    color_list <- color_list[1:length(colors)]
    names(color_list) <- colors
    #colors <- recode(colors, !!!color_list)
    
    plt <- plt +
      scale_fill_manual(values = color_list, guide = "none")
  } else {
    plt <- plt +
      scale_fill_brewer(palette = "Set1", guide = "none")
  }
  
  if (fix_yaxis) {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6),
                      ylim = ylimits)
  } else {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6))
  }
  
  if (! is.null(aspect_ratio)) {
    plt <- plt +
      theme(aspect.ratio = aspect_ratio)
  }
  
  plot(plt)
  
}


# Plot
PlotDataTracksLight(input_tib = samples,
                    exp_names = c("Pool3_cl70_CAST", "Pool3_cl70_129S1", "Pool3_cl83_CAST", "Pool3_cl83_129S1"),
                    color_groups = c(Pool3_cl70_CAST = "pA-DamID", Pool3_cl70_129S1 = "pA-DamID", Pool3_cl83_CAST = "pA-DamID", Pool3_cl83_129S1 = "pA-DamID") ,
                    plot_chr = "chr9", plot_start = 109437608, plot_end = 119448158,
                    color_list = c("gray"),
                    #color_list = brewer.pal(3, "Paired"),
                    aspect_ratio = 1/5,
                    smooth = 7,
                    #fix_yaxis = F,
                    lighten_negative = T,
                    raster = T)

# ggsave("FigS8B_LD20230809_CRISPR_isol_pool3.pdf", path = "./output/", height = 15, width = 20)


```


# Extended Data 5D - Deletion in the strong iLAD - Pool4
```{r}
## deletion coordinate

del_loc_pool4 = data.frame(sample = c('1', '2'),
           x = c(110927601, 112360112),
           y = rep(1.4, 2),
           xend = c(112154177, 114785359),
           yend = rep(1.4, 2))


# Function
PlotDataTracksLight <- function(input_tib, exp_names, color_groups, 
                                centromeres = NULL, plot_chr = "chr1", 
                                plot_start = 1, plot_end = 500e6,
                                smooth = 1, color_list = NULL,
                                fix_yaxis = F, aspect_ratio = NULL,
                                lighten_negative = F, raster = F) {
  
  # Get the scores for the samples
  tib_plot <- input_tib %>%
    dplyr::select(seqnames, start, end, 
                  all_of(exp_names))
  
  if (smooth > 1) {
    tib_plot <- tib_plot %>%
      mutate_at(vars(contains("_")), 
                runmean, k = smooth)
  }
  
  # Filter for plotting window
  tib_plot <- tib_plot %>%
    filter(seqnames == plot_chr,
           start >= plot_start,
           end <= plot_end)
  
  # Gather
  tib_gather <- tib_plot %>%
    gather(key, value, -seqnames, -start, -end) %>%
    mutate(key = factor(key, levels = exp_names),
           fill_column = color_groups[match(key, names(color_groups))],
           fill_column = factor(fill_column, levels = unique(color_groups)))
  
  # If desired, make negative values a lighter shade to improve visualization
  if (lighten_negative) {
    tib_gather <- tib_gather %>%
      mutate(fill_column = interaction(fill_column,
                                       value < 0))
  }
  
  
  
  # Plot
  ylimits <- quantile(tib_gather$value, c(0.001, 0.999), na.rm = T)
  fill_column <- NULL
  
  plt <- tib_gather %>% 
    ggplot(aes(fill = fill_column))
  
  
  # Set all counts tracks to the same limits
  if (raster) {
    plt <- plt + 
      rasterize(geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                              ymin = 0, ymax = value)),
                dpi = 300)
  } else {
    plt <- plt + 
      geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                    ymin = 0, ymax = value))
  }
  
  plt <- plt + 
    geom_hline(yintercept = 0, size = 0.5) +
    #geom_segment(data=del_loc[1,], mapping=aes(x=x/1e6, xend=xend/1e6, y=y, yend=yend), linewidth = 1, color = "#6BAED6")+
    geom_vline(xintercept = del_loc_pool4[1,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool4[1,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool4[2,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool4[2,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    facet_grid(key ~ ., scales = "free_y") +
    xlab(paste0(plot_chr, " (Mb)")) +
    ylab("counts (Dam + LB1)") +
    #scale_x_continuous(expand = c(0, 0)) + 
    #scale_y_continuous(expand = c(0.025, 0.025), limits = c(-1.5, 1.5)) +
    theme_bw() +
    theme(text = element_text(size = 50))
  
  # Centromeres
  if (! is.null(centromeres)) {
    centromeres.plt <- as_tibble(centromeres) %>%
      filter(seqnames == plot_chr) %>%
      gather(key_centromeres, value, start, end)
    
    plt <- plt +
      geom_line(data = centromeres.plt, 
                aes(x = value / 1e6, y = 0),
                color = "black", size = 2)
  }
  
  if (! is.null(color_list)) {
    
    if (lighten_negative) {
      color_list <- c(color_list,
                      lighten(color_list, amount = 0.5))
    }
    
    colors <- levels(tib_gather$fill_column)
    
    color_list <- color_list[1:length(colors)]
    names(color_list) <- colors
    #colors <- recode(colors, !!!color_list)
    
    plt <- plt +
      scale_fill_manual(values = color_list, guide = "none")
  } else {
    plt <- plt +
      scale_fill_brewer(palette = "Set1", guide = "none")
  }
  
  if (fix_yaxis) {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6),
                      ylim = ylimits)
  } else {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6))
  }
  
  if (! is.null(aspect_ratio)) {
    plt <- plt +
      theme(aspect.ratio = aspect_ratio)
  }
  
  plot(plt)
  
}


# Plot
PlotDataTracksLight(input_tib = samples,
                    exp_names = c("Pool4_cl81_CAST", "Pool4_cl81_129S1"),
                    color_groups = c(Pool4_cl81_CAST = "pA-DamID", Pool4_cl81_129S1 = "pA-DamID") ,
                    plot_chr = "chr9", plot_start = 109437608, plot_end = 119448158,
                    color_list = c("gray"),
                    #color_list = brewer.pal(3, "Paired"),
                    aspect_ratio = 1/5,
                    smooth = 7,
                    #fix_yaxis = F,
                    lighten_negative = T,
                    raster = T)

# ggsave("FigS8B_LD20230809_CRISPR_isol_pool4.pdf", path = "./output/", height = 10, width = 20)

```


# Extended Data 5G - Deletion iclose to LAD4 - Pool7
```{r}

## deletion coordinate

del_loc_pool7 = data.frame(sample = c('1', '2'),
           x = c(110927601, 112439588),
           y = rep(1.4, 2),
           xend = c(112653616, 116258017),
           yend = rep(1.4, 2))


# Function
PlotDataTracksLight <- function(input_tib, exp_names, color_groups, 
                                centromeres = NULL, plot_chr = "chr1", 
                                plot_start = 1, plot_end = 500e6,
                                smooth = 1, color_list = NULL,
                                fix_yaxis = F, aspect_ratio = NULL,
                                lighten_negative = F, raster = F) {
  
  # Get the scores for the samples
  tib_plot <- input_tib %>%
    dplyr::select(seqnames, start, end, 
                  all_of(exp_names))
  
  if (smooth > 1) {
    tib_plot <- tib_plot %>%
      mutate_at(vars(contains("_")), 
                runmean, k = smooth)
  }
  
  # Filter for plotting window
  tib_plot <- tib_plot %>%
    filter(seqnames == plot_chr,
           start >= plot_start,
           end <= plot_end)
  
  # Gather
  tib_gather <- tib_plot %>%
    gather(key, value, -seqnames, -start, -end) %>%
    mutate(key = factor(key, levels = exp_names),
           fill_column = color_groups[match(key, names(color_groups))],
           fill_column = factor(fill_column, levels = unique(color_groups)))
  
  # If desired, make negative values a lighter shade to improve visualization
  if (lighten_negative) {
    tib_gather <- tib_gather %>%
      mutate(fill_column = interaction(fill_column,
                                       value < 0))
  }
  
  
  
  # Plot
  ylimits <- quantile(tib_gather$value, c(0.001, 0.999), na.rm = T)
  fill_column <- NULL
  
  plt <- tib_gather %>% 
    ggplot(aes(fill = fill_column))
  
  
  # Set all counts tracks to the same limits
  if (raster) {
    plt <- plt + 
      rasterize(geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                              ymin = 0, ymax = value)),
                dpi = 300)
  } else {
    plt <- plt + 
      geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                    ymin = 0, ymax = value))
  }
  
  plt <- plt + 
    geom_hline(yintercept = 0, size = 0.5) +
    #geom_segment(data=del_loc[1,], mapping=aes(x=x/1e6, xend=xend/1e6, y=y, yend=yend), linewidth = 1, color = "#6BAED6")+
    geom_vline(xintercept = del_loc_pool7[1,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool7[1,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool7[2,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool7[2,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    facet_grid(key ~ ., scales = "free_y") +
    xlab(paste0(plot_chr, " (Mb)")) +
    ylab("counts (Dam + LB1)") +
    #scale_x_continuous(expand = c(0, 0)) + 
    #scale_y_continuous(expand = c(0.025, 0.025), limits = c(-1.5, 1.5)) +
    theme_bw() +
    theme(text = element_text(size = 50))
  
  # Centromeres
  if (! is.null(centromeres)) {
    centromeres.plt <- as_tibble(centromeres) %>%
      filter(seqnames == plot_chr) %>%
      gather(key_centromeres, value, start, end)
    
    plt <- plt +
      geom_line(data = centromeres.plt, 
                aes(x = value / 1e6, y = 0),
                color = "black", size = 2)
  }
  
  if (! is.null(color_list)) {
    
    if (lighten_negative) {
      color_list <- c(color_list,
                      lighten(color_list, amount = 0.5))
    }
    
    colors <- levels(tib_gather$fill_column)
    
    color_list <- color_list[1:length(colors)]
    names(color_list) <- colors
    #colors <- recode(colors, !!!color_list)
    
    plt <- plt +
      scale_fill_manual(values = color_list, guide = "none")
  } else {
    plt <- plt +
      scale_fill_brewer(palette = "Set1", guide = "none")
  }
  
  if (fix_yaxis) {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6),
                      ylim = ylimits)
  } else {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6))
  }
  
  if (! is.null(aspect_ratio)) {
    plt <- plt +
      theme(aspect.ratio = aspect_ratio)
  }
  
  plot(plt)
  
}


# Plot
PlotDataTracksLight(input_tib = samples,
                    exp_names = c("Pool7_cl84_CAST", "Pool7_cl84_129", "Pool7_cl127_CAST", "Pool7_cl127_129"),
                    color_groups = c(Pool7_cl84_CAST = "pA-DamID", Pool7_cl84_129 = "pA-DamID", Pool7_cl127_CAST = "pA-DamID", Pool7_cl127_129 = "pA-DamID") ,
                    plot_chr = "chr9", plot_start = 109437608, plot_end = 119448158,
                    color_list = c("gray"),
                    #color_list = brewer.pal(3, "Paired"),
                    aspect_ratio = 1/5,
                    smooth = 7,
                    #fix_yaxis = F,
                    lighten_negative = T,
                    raster = T)

# ggsave("FigS8E_LD20230809_CRISPR_isol_pool7.pdf", path = "./output/", height = 15, width = 20)


```


# Extended Data 5G - Deletions close to LAD4 - Pool8
```{r}

## deletion coordinate

del_loc_pool8 = data.frame(sample = c('1', '2'),
           x = c(110927601, 112360112),
           y = rep(1.4, 2),
           xend = c(112153267, 116258017),
           yend = rep(1.4, 2))


# Function
PlotDataTracksLight <- function(input_tib, exp_names, color_groups, 
                                centromeres = NULL, plot_chr = "chr1", 
                                plot_start = 1, plot_end = 500e6,
                                smooth = 1, color_list = NULL,
                                fix_yaxis = F, aspect_ratio = NULL,
                                lighten_negative = F, raster = F) {
  
  # Get the scores for the samples
  tib_plot <- input_tib %>%
    dplyr::select(seqnames, start, end, 
                  all_of(exp_names))
  
  if (smooth > 1) {
    tib_plot <- tib_plot %>%
      mutate_at(vars(contains("_")), 
                runmean, k = smooth)
  }
  
  # Filter for plotting window
  tib_plot <- tib_plot %>%
    filter(seqnames == plot_chr,
           start >= plot_start,
           end <= plot_end)
  
  # Gather
  tib_gather <- tib_plot %>%
    gather(key, value, -seqnames, -start, -end) %>%
    mutate(key = factor(key, levels = exp_names),
           fill_column = color_groups[match(key, names(color_groups))],
           fill_column = factor(fill_column, levels = unique(color_groups)))
  
  # If desired, make negative values a lighter shade to improve visualization
  if (lighten_negative) {
    tib_gather <- tib_gather %>%
      mutate(fill_column = interaction(fill_column,
                                       value < 0))
  }
  
  
  
  # Plot
  ylimits <- quantile(tib_gather$value, c(0.001, 0.999), na.rm = T)
  fill_column <- NULL
  
  plt <- tib_gather %>% 
    ggplot(aes(fill = fill_column))
  
  
  # Set all counts tracks to the same limits
  if (raster) {
    plt <- plt + 
      rasterize(geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                              ymin = 0, ymax = value)),
                dpi = 300)
  } else {
    plt <- plt + 
      geom_rect(aes(xmin = start / 1e6, xmax = end / 1e6, 
                    ymin = 0, ymax = value))
  }
  
  plt <- plt + 
    geom_hline(yintercept = 0, size = 0.5) +
    #geom_segment(data=del_loc[1,], mapping=aes(x=x/1e6, xend=xend/1e6, y=y, yend=yend), linewidth = 1, color = "#6BAED6")+
    geom_vline(xintercept = del_loc_pool8[1,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool8[1,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool8[2,]$x/1e6, size = 0.5, col = "black", linetype = "dashed") +
    geom_vline(xintercept = del_loc_pool8[2,]$xend/1e6, size = 0.5, col = "black", linetype = "dashed") +
    facet_grid(key ~ ., scales = "free_y") +
    xlab(paste0(plot_chr, " (Mb)")) +
    ylab("counts (Dam + LB1)") +
    #scale_x_continuous(expand = c(0, 0)) + 
    #scale_y_continuous(expand = c(0.025, 0.025), limits = c(-1.5, 1.5)) +
    theme_bw() +
    theme(text = element_text(size = 50))
  
  # Centromeres
  if (! is.null(centromeres)) {
    centromeres.plt <- as_tibble(centromeres) %>%
      filter(seqnames == plot_chr) %>%
      gather(key_centromeres, value, start, end)
    
    plt <- plt +
      geom_line(data = centromeres.plt, 
                aes(x = value / 1e6, y = 0),
                color = "black", size = 2)
  }
  
  if (! is.null(color_list)) {
    
    if (lighten_negative) {
      color_list <- c(color_list,
                      lighten(color_list, amount = 0.5))
    }
    
    colors <- levels(tib_gather$fill_column)
    
    color_list <- color_list[1:length(colors)]
    names(color_list) <- colors
    #colors <- recode(colors, !!!color_list)
    
    plt <- plt +
      scale_fill_manual(values = color_list, guide = "none")
  } else {
    plt <- plt +
      scale_fill_brewer(palette = "Set1", guide = "none")
  }
  
  if (fix_yaxis) {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6),
                      ylim = ylimits)
  } else {
    plt <- plt + 
      coord_cartesian(xlim = c(max(c(plot_start,
                                     min(tib_gather$start))) / 1e6,
                               min(c(plot_end,
                                     max(tib_gather$end))) / 1e6))
  }
  
  if (! is.null(aspect_ratio)) {
    plt <- plt +
      theme(aspect.ratio = aspect_ratio)
  }
  
  plot(plt)
  
}


PlotDataTracksLight(input_tib = samples,
                    exp_names = c("Pool8_cl58_CAST", "Pool8_cl58_129"),
                    color_groups = c(Pool8_cl58_CAST = "pA-DamID", Pool8_cl58_129 = "pA-DamID") ,
                    plot_chr = "chr9", plot_start = 109437608, plot_end = 119448158,
                    color_list = c("gray"),
                    #color_list = brewer.pal(3, "Paired"),
                    aspect_ratio = 1/5,
                    smooth = 7,
                    #fix_yaxis = F,
                    lighten_negative = T,
                    raster = T)


# ggsave("FigS8E_LD20230809_CRISPR_isol_pool8.pdf", path = "./output/", height = 10, width = 20)

```


# Extended Data 5F - right
## Pool3 - all data
```{r}
# Load raw data generated from the domainograms
load("/DATA/usr/l.dauban/projects/pA-DamID/E2316_LAD_isolation_reseq/stat_tests/Domainograms/Pool3_1/domainograms.RData")
Pool3_Control = sDamID.Control
Pool3_Exp = sDamID.Exp
Pool3_DG = DG.Exp

# Add LAD feature
Pool3.ROI = GRanges(seqnames = "chr9", ranges = IRanges(110927601, 112439588))

Pool3_Exp <- Pool3_Exp %>% mutate(LAD = ifelse(Pool3_Exp$logratio > 0, "LAD", "iLAD"))
Pool3_Exp[which(seqnames(Pool3_Exp) == "chr9" & start(Pool3_Exp) > start(Pool3.ROI) & start(Pool3_Exp) < end(Pool3.ROI))]$LAD <- "ROI"

# filter on plotted window
window = data.frame(start = 109937608,  end = 119448158)

Pool3_Exp.window <- Pool3_Exp %>% filter(seqnames == "chr9" & start > window$start & start < window$end & logratio != "NA") %>% as_tibble()

# sample dataset
pool3.nrow <- Pool3_Exp.window %>% filter(LAD == "ROI") %>% summarise(nrow = nrow(.))

set.seed(1000)

Pool3_Exp.window.iLAD <- Pool3_Exp.window %>% filter(LAD == "iLAD") %>% slice_sample(n= pool3.nrow$nrow)
Pool3_Exp.window.LAD <- Pool3_Exp.window %>% filter(LAD == "LAD") %>% slice_sample(n= pool3.nrow$nrow)
Pool3_Exp.window.ROI <- Pool3_Exp.window %>% filter(LAD == "ROI")

```

## Pool4 - all data
```{r}
# Load smoothed data generated from the domainograms
load("/DATA/usr/l.dauban/projects/pA-DamID/E2316_LAD_isolation_reseq/stat_tests/Domainograms/Pool4_1/domainograms.RData")
Pool4_Control = sDamID.Control
Pool4_Exp = sDamID.Exp
Pool4_DG = DG.Exp

# Add LAD feature
Pool4.ROI = GRanges(seqnames = "chr9", ranges = IRanges(110927601, 112154177))

Pool4_Exp <- Pool4_Exp %>% mutate(LAD = ifelse(Pool4_Exp$logratio > 0, "LAD", "iLAD"))
Pool4_Exp[which(seqnames(Pool4_Exp) == "chr9" & start(Pool4_Exp) > start(Pool4.ROI) & start(Pool4_Exp) < end(Pool4.ROI))]$LAD <- "ROI"

# filter on plotted window
window = data.frame(start = 109937608,  end = 119448158)

Pool4_Exp.window <- Pool4_Exp %>% filter(seqnames == "chr9" & start > window$start & start < window$end & logratio != "NA") %>% as_tibble()

# sample dataset
Pool4.nrow <- Pool4_Exp.window %>% filter(LAD == "ROI") %>% summarise(nrow = nrow(.))

Pool4_Exp.window.iLAD <- Pool4_Exp.window %>% filter(LAD == "iLAD") %>% slice_sample(n= Pool4.nrow$nrow)
Pool4_Exp.window.LAD <- Pool4_Exp.window %>% filter(LAD == "LAD") %>% slice_sample(n= Pool4.nrow$nrow)
Pool4_Exp.window.ROI <- Pool4_Exp.window %>% filter(LAD == "ROI")

```

## Pool3 - GATC fragments every 2.5 kb
```{r}
# loop to select gatc fragments separated by at least 2.5 kb
vect1 = 2:nrow(Pool3_Exp.window.ROI)
Pool3_Exp.window.ROI_2 = Pool3_Exp.window.ROI[1,]

for (i in vect1){
  if (Pool3_Exp.window.ROI[i,]$start - Pool3_Exp.window.ROI_2[nrow(Pool3_Exp.window.ROI_2),]$start < 2500) {
    next
  } 
  Pool3_Exp.window.ROI_2 = rbind(Pool3_Exp.window.ROI_2, Pool3_Exp.window.ROI[i,])
  }

```

## Pool4 - GATC fragments every 2.5 kb
```{r}
# loop to select gatc fragments separated by at least 2.5 kb
vect1 = 2:nrow(Pool4_Exp.window.ROI)
Pool4_Exp.window.ROI_2 = Pool4_Exp.window.ROI[1,]

for (i in vect1){
  if (Pool4_Exp.window.ROI[i,]$start - Pool4_Exp.window.ROI_2[nrow(Pool4_Exp.window.ROI_2),]$start < 2500) {
    next
  } 
  Pool4_Exp.window.ROI_2 = rbind(Pool4_Exp.window.ROI_2, Pool4_Exp.window.ROI[i,])
  }

```

## Compare pool3 and pool4
```{r}
# Normalise pool3 data
Q005.pool3 = quantile((mcols(Pool3_Exp)$logratio + mcols(Pool3_Control)$logratio) / 2, 0.05, na.rm=TRUE)
Pool3_Exp.window.ROI.norm <- Pool3_Exp.window.ROI_2 %>% rowwise() %>% mutate(logratio = logratio - Q005.pool3)
Pool3_Exp.window.ROI.norm$pool <- "Pool3"

# Normalise pool4 data
Q005.pool4 = quantile((mcols(Pool4_Exp)$logratio + mcols(Pool4_Control)$logratio) / 2, 0.05, na.rm=TRUE)
Pool4_Exp.window.ROI.norm <- Pool4_Exp.window.ROI_2 %>% rowwise() %>% mutate(logratio = logratio - Q005.pool4)
Pool4_Exp.window.ROI.norm$pool <- "Pool4"

# Combine
ROI.norm.comb <- rbind(Pool3_Exp.window.ROI.norm, Pool4_Exp.window.ROI.norm)

# Plot
ROI.norm.comb %>%
  ggplot(aes(x= pool, y= logratio)) + 
  geom_violin(aes(color = pool), show.legend = "none") +
  geom_beeswarm(aes(color = pool), alpha = 0.1, priority ="random", show.legend = "none") +
  geom_signif(test = "wilcox.test", test.args = list(alternative = c("greater")), comparisons = list(c("Pool3", "Pool4")))+
  stat_summary(fun=mean, geom="crossbar", width=0.2)+
  labs(title = "ROI comparaison - raw data - GATC fragments 2.5 kb apart",
       x = "",
       y = "normalised pA-DamID (z-score)") +
  scale_color_manual(labels = c("Pool3", "Pool4"), values = c('#1D899B', '#A7CEE1'))+
  scale_x_discrete(labels=c('R4-5', 'R2-3')) +
  theme_bw()

# ggsave("FigS8Dter_LD20250501.pdf", path = "./output/", height = 4, width = 6)

```


# Extended Data 5F - left
```{r}
# loop to select gatc fragments separated by at least 2.5 kb
## ROI
vect1 = 2:nrow(Pool3_Exp.window.ROI)
Pool3_Exp.window.ROI_2 = Pool3_Exp.window.ROI[1,]

for (i in vect1){
  if (Pool3_Exp.window.ROI[i,]$start - Pool3_Exp.window.ROI_2[nrow(Pool3_Exp.window.ROI_2),]$start < 2500) {
    next
  } 
  Pool3_Exp.window.ROI_2 = rbind(Pool3_Exp.window.ROI_2, Pool3_Exp.window.ROI[i,])
  }


## LAD
Pool3_Exp.window.LAD.2.5 <- Pool3_Exp.window %>% filter(LAD == "LAD") 
Pool3_Exp.window.LAD.2.5_2 <- Pool3_Exp.window.LAD.2.5[1,]
vect2 <- 2: nrow(Pool3_Exp.window.LAD.2.5)

for (i in vect2){
  if (Pool3_Exp.window.LAD.2.5[i,]$start - Pool3_Exp.window.LAD.2.5_2[nrow(Pool3_Exp.window.LAD.2.5_2),]$start < 2500) {
    next
  } 
  Pool3_Exp.window.LAD.2.5_2 = rbind(Pool3_Exp.window.LAD.2.5_2, Pool3_Exp.window.LAD.2.5[i,])
}

## check loop
#Pool3_Exp.window.LAD.2.5_2 %>% rowwise() %>% mutate(dist = start - 109940861)


## iLAD
Pool3_Exp.window.iLAD.2.5 <- Pool3_Exp.window %>% filter(LAD == "iLAD") 
Pool3_Exp.window.iLAD.2.5_2 <- Pool3_Exp.window.iLAD.2.5[1,]
vect2 <- 2: nrow(Pool3_Exp.window.iLAD.2.5)

for (i in vect2){
  if (Pool3_Exp.window.iLAD.2.5[i,]$start - Pool3_Exp.window.iLAD.2.5_2[nrow(Pool3_Exp.window.iLAD.2.5_2),]$start < 2500) {
    next
  } 
  Pool3_Exp.window.iLAD.2.5_2 = rbind(Pool3_Exp.window.iLAD.2.5_2, Pool3_Exp.window.iLAD.2.5[i,])
}

## check loop
#Pool3_Exp.window.iLAD.2.5_2 %>% rowwise() %>% mutate(dist = start - 109938839)


# Combine
Pool3_Exp.window.comb.2.5 <- rbind(Pool3_Exp.window.iLAD.2.5_2, Pool3_Exp.window.LAD.2.5_2, Pool3_Exp.window.ROI_2)

# Plot
Pool3_Exp.window.comb.2.5 %>% mutate(LAD = factor(LAD, levels = c("iLAD", "ROI", "LAD"))) %>%
  ggplot(aes(x= LAD, y= logratio)) + 
  geom_violin(aes(color = LAD), show.legend = "none") +
  geom_beeswarm(aes(color = LAD), cex = 0.23, alpha = 0.1, priority ="random", show.legend = "none") +
  stat_summary(fun=mean, geom="crossbar", width=0.2)+
  geom_signif(test = "wilcox.test", test.args = list(alternative = c("greater")), comparisons = list(c("ROI", "iLAD"), c("LAD", "ROI")))+
  labs(title = "Pool3 - raw data - GATC fragments 2.5 kb apart",
       x = "",
       y = "pA-DamID (z-score)") +
  theme_bw()+
  #scale_y_continuous(breaks=seq(-6,40,3))+
  scale_color_manual(labels = c("iLAD","ROI", "LAD"), values = c("#F4C374", '#1D899B', '#A7CEE1'))+
  scale_x_discrete(labels=c("iLAD", 'R4-5', 'LAD'), position = "bottom") +
  scale_y_break(c(4, 26), ticklabels = c(-6, 40, 3))
  


# ggsave("FigS8D_LD20250501.pdf", path = "./output/", height = 4, width = 6)


```


# Extended Data 5F - middle
```{r}
# loop to select gatc fragments separated by at least 2.5 kb
## ROI
vect1 = 2:nrow(Pool4_Exp.window.ROI)
Pool4_Exp.window.ROI_2 = Pool4_Exp.window.ROI[1,]

for (i in vect1){
  if (Pool4_Exp.window.ROI[i,]$start - Pool4_Exp.window.ROI_2[nrow(Pool4_Exp.window.ROI_2),]$start < 2500) {
    next
  } 
  Pool4_Exp.window.ROI_2 = rbind(Pool4_Exp.window.ROI_2, Pool4_Exp.window.ROI[i,])
  }


## LAD
Pool4_Exp.window.LAD.2.5 <- Pool4_Exp.window %>% filter(LAD == "LAD") 
Pool4_Exp.window.LAD.2.5_2 <- Pool4_Exp.window.LAD.2.5[1,]
vect2 <- 2: nrow(Pool4_Exp.window.LAD.2.5)

for (i in vect2){
  if (Pool4_Exp.window.LAD.2.5[i,]$start - Pool4_Exp.window.LAD.2.5_2[nrow(Pool4_Exp.window.LAD.2.5_2),]$start < 2500) {
    next
  } 
  Pool4_Exp.window.LAD.2.5_2 = rbind(Pool4_Exp.window.LAD.2.5_2, Pool4_Exp.window.LAD.2.5[i,])
}

## check loop
#Pool4_Exp.window.LAD.2.5_2 %>% rowwise() %>% mutate(dist = start - 109940861)


## iLAD
Pool4_Exp.window.iLAD.2.5 <- Pool4_Exp.window %>% filter(LAD == "iLAD") 
Pool4_Exp.window.iLAD.2.5_2 <- Pool4_Exp.window.iLAD.2.5[1,]
vect2 <- 2: nrow(Pool4_Exp.window.iLAD.2.5)

for (i in vect2){
  if (Pool4_Exp.window.iLAD.2.5[i,]$start - Pool4_Exp.window.iLAD.2.5_2[nrow(Pool4_Exp.window.iLAD.2.5_2),]$start < 2500) {
    next
  } 
  Pool4_Exp.window.iLAD.2.5_2 = rbind(Pool4_Exp.window.iLAD.2.5_2, Pool4_Exp.window.iLAD.2.5[i,])
}

## check loop
#Pool4_Exp.window.iLAD.2.5_2 %>% rowwise() %>% mutate(dist = start - 109938839)


# Combine
Pool4_Exp.window.comb.2.5 <- rbind(Pool4_Exp.window.iLAD.2.5_2, Pool4_Exp.window.LAD.2.5_2, Pool4_Exp.window.ROI_2)

# Plot
Pool4_Exp.window.comb.2.5 %>% mutate(LAD = factor(LAD, levels = c("iLAD", "ROI", "LAD"))) %>%
  ggplot(aes(x= LAD, y= logratio)) + 
  geom_violin(aes(color = LAD), show.legend = "none") +
  geom_beeswarm(aes(color = LAD), cex = 0.35, alpha = 0.1, priority ="random", show.legend = "none") +
  stat_summary(fun=mean, geom="crossbar", width=0.2) +
  geom_signif(test = "wilcox.test", test.args = list(alternative = c("greater")), comparisons = list(c("ROI", "iLAD"), c("LAD", "ROI")))+
  labs(title = "Pool4 - raw data - GATC fragments 2.5 kb apart",
       x = "",
       y = "pA-DamID (z-score)") +
  coord_cartesian(ylim = c(-8, 5))+
  scale_color_manual(labels = c("iLAD","ROI", "LAD"), values = c("#F4C374", '#A7CEE1', '#A7CEE1'))+
  scale_x_discrete(labels=c("iLAD", 'R2-3', 'LAD')) +
  theme_bw()
  
# ggsave("FigS8Dbis_LD20250501.pdf", path = "./output/", height = 4, width = 6)

```





